### 2020-10-08 paper/natastron/response/response.tex

\noindent \textbf{With photometry, rotation is much easier to measure for the stars that are active and faster rotating. Is there a similar bias in the case of seismology? }

In short, yes, there are biases at play, but we don’t think these will affect our results. We’ve discussed them below, and have included a version of this discussion in the \textbf{Methods} section of the new draft.

\textit{Bias in rotation detection:} stars that are rotating very slowly will show very small splittings, which may be indistinguishable from a non-rotating case, whereas stars that are spinning very fast may find that their splitting is so wide that they cross over with split modes at different radial orders. We’ve done some calculations to show that this shouldn’t affect the region of rotation we’re interested in.
\begin{enumerate}
\item \textit{Fast rotating stars}: in principle, a star could rotate fast enough that the highest-frequency peak in a split dipole ($\ell=2$) mode would overlap with the radial ($\ell=0$) mode. This would occur if $2\nu_{\rm{s}} > \delta\nu_{02}$. For the star in our sample with the smallest $\delta\nu_{02}$ (so the highest risk of this happening), this limit is at 8.8 days. However for the star with the largest $\delta\nu_{02}$, this lies at ~2 days.

In practice, we think that the model would properly fit a spectrum where this kind of mode-overlapping was happening. The $\ell=0$ modes don’t split, and so if a $\ell=2$ mode were split so far that overlap was occurring, the $\ell=0$ mode would appear broadened or asymmetrical, which is not degenerate with any other model states. There would still be a constraint on the splitting from the lower-frequency peaks. We can envision there being an issue if an $\ell=2$ mode is overlapping with an $\ell=1$ mode at lower frequencies as well, however this would only occur at a rotation rate of 2 days or faster for the star with the smallest $\delta\nu_{01}$.

@@

In our sample, there are 9 stars for which we measured splittings faster than the limit of $2\nu_s > \delta\nu{02}$. All these stars showed good agreement with previous work, and were well converged, which implies that asteroseismic models such as ours can handle such mode overlap. But as far as our conclusions are concerned, all 9 are either Hot or Subgiant stars, which we show don’t impact our conclusions either way in the paper.

\item \textit{Slow rotating stars:} Below, the reviewer raises concerns that for a limit of $\nu_s < 2\Gamma$ (when the splitting is smaller than the double the linewidth), splitting may not be accurately constrained. We dont believe this is the fundamental limit on this measurement, as splitting instead more frequently causes a change in the power distribution in frequency of the modes. Detection of this change makes it possible to measure seismic rotation even when the split components are not fully separated.  It is also worth noting that the non-split radial ($\ell=0$) modes provide strong constraints on the variation of linewidth with frequency. We discuss this more below. If there is to be a hard limit at which the the effects of splitting can not be measured, we suggest that it is when it would be impossible to resolve it, so where $\nu_s < 2/T$, two times the frequency bin width. The bin width is set by observing time, so to make an conservative estimate, we can take our star with the shortest observing time  (0.49 years). For this star, the limit on measuring rotation would be ~89 days (and going up for longer observing baselines). Of course, as discussed below, as you get to slower rotation rates it becomes harder to constrain the small rate of mode splitting and so the uncertainty will increase. We believe this is dealt with appropriately in our model comparison through the use of hierarchical models.
\end{enumerate}

@@

With regards to the rotation models: we agree, which is why we want to explore this option in a future paper, as mentioned in the conclusions. It is our opinion that performing this comparison in a separate work would be more appropriate. The two models we use to compare to our data in this work have already been used in the past to forward-model the Kepler field (see van Saders et al. (2019)), so their inclusion here is straightforward. It is also worth pointing out that most rotation models without weakened magnetic braking will have pretty similar predictions in this regime our sample occupies anyway, as they are all calibrated to reproduce the Sun (and at younger ages, clusters), and so the largest difference between models will come from the inclusion of a change in the braking law. It’s not that we think that such a comparison isn’t important -- on the contrary -- but we think it should be explored in a separate paper with more of a focus on the differences in theoretical models, and including a much broader range of models both with- and without changes to the braking.

We’ve tried to be careful throughout and reiterate that this is only a comparison of two models, so that there isn’t any confusion for the readers.\\

\noindent\textbf{One may fear that seismology works only for $\nu_s / \Gamma$ large (ratio of rotational splitting to mode line width, not provided). 
\begin{itemize}
\item How many stars have $\nu_s /  \Gamma < 2$ here (the problematic cases)?
\item How many of these are slow rotators? 
\end{itemize}
}

That seismic rotation can only be probed in cases where split components are fully separated from one another, as the reviewer is suggesting, is a common misconception. Asteroseismic splitting is rarely larger than double the linewidth (in our sample this is only the case for a handful of the fastest rotators). Instead, rotational splitting changes the distribution of a mode's power with frequency, in a way that can be disentangled. This takes a specific form depending on the angular degree of the mode and the inclination angle of the star. This is why marginalising over inclination angle is important, because only by constructing a model that accounts for inclination angle and rotation together can you accurately represent how rotation affects the modes.

It is also worth noting that our fitting method marginalises over inclination angle, rotational splitting and linewidth, and so the final rotational period measurements have uncertainties that accurately reflect the uncertainty associated with the slow rotation only having a small effect on the power distribution of the modes of oscillation. To be clear, there is no boundary beyond which this methodology of measuring asteroseismic rotation no longer works, until you start pushing up against the frequency resolution of the power spectrum (as discussed above).

### 2020-10-08 paper/natastron/methods.tex
bill comments done

	\item \textit{Slow rotating stars:} Except for the most rapidly rotating cases, asteroseismic mode splitting is detected by a broadening of the mode frequencies as the split components begin to separate from the central mode. If there is to be hard limit at which this measurement is not possible, it should be in the case that $\nu_{\rm s} < 2/T$, where $T$ is the observation time, and $1/T$ is the frequency bin width. For the star in our sample with the shortest observing time, this limit would be $\sim 89$ days, which quickly rises for longer observing baselines. While this constitutes a hard limit, slower rotation rates will become harder and harder to constrain as the rate of splitting becomes smaller. A benefit of the Bayesian approach used in this paper is that it should accurately reflect the increased uncertainty associated with the small rotational splitting.
\end{itemize}

>>>>

	\item \textit{Slow rotating stars:} Except for the most rapidly rotating cases, asteroseismic mode splitting is detected by a change in the distribution of the power of mode frequencies as the split components begin to separate from the central mode. If there is to be hard limit at which this measurement is not possible, it should be in the case that $\nu_{\rm s} < 2/T$, where $T$ is the observation time, and $1/T$ is the frequency bin width. For the star in our sample with the shortest observing time, this limit would be $\sim 89$ days, which quickly rises for longer observing baselines. While this constitutes a hard limit, slower rotation rates will become harder and harder to constrain as the rate of splitting becomes smaller. A benefit of the Bayesian approach used in this paper is that it should accurately reflect the increased uncertainty associated with the small rotational splitting.
\end{itemize}
